The pollination trade-off

### 2019-04-15 paper/cover-letter.Rnw
Ignore tex file of cover letter

Lastly, please note that the data used in this manuscript has been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors, however the enclosed work represents a novel contribution for all involved and no related work published, in press, or submitted during this or last year has been cited.

>>>>

Lastly, please note that the data used in this manuscript has been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors.
However the enclosed work represents a novel contribution for all involved and no related work published, in press, or submitted during this or last year has been cited.
